Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2019-12-24 analysis/paper/paper.Rmd
added section to re-create extrapolation model fit table with r-squared values

>>>>

```{r extrap-table}
mod_fit_df = model_svy_df %>%
  select(response, data) %>%
  unnest(cols = data) %>%
  select(response, obs = qrf_cap) %>%
  group_by(response) %>%
  mutate(id = 1:n()) %>%
  left_join(model_svy_df %>%
              mutate(pred_full = map(mod_full,
                                     .f = function(x) {
                                       predict(x,
                                               type = 'response') %>%
                                         as_tibble() %>%
                                         rename(pred_full = response,
                                                pred_full_se = SE)
                                     }),
                     pred_no_champ = map(mod_no_champ,
                                         .f = function(x) {
                                           predict(x,
                                                   type = 'response') %>%
                                             as_tibble() %>%
                                             rename(pred_no_champ = response,
                                                    pred_no_champ_se = SE)
                                         })) %>%
              select(response, starts_with("pred")) %>%
              unnest(cols = starts_with("pred")) %>%
              group_by(response) %>%
              mutate(id = 1:n())) %>%
  ungroup()

# mod_fit_df %>%
#   group_by(response) %>%
#   summarise(r2_full = cor(obs, pred_full)^2,
#             r2_no_champ = cor(obs, pred_no_champ)^2) %>%
#   gather(type, r2, -response) %>%
#   mutate(model = if_else(grepl('no_champ', type),
#                          'non-CHaMP',
#                          'CHaMP'),
#          type = if_else(grepl('adj', type),
#                         'Adjusted R2',
#                         'R2')) %>%
#   spread(type, r2) %>%
#   mutate(response = recode(response,
#                            'chnk_per_m' = 'fish/m',
#                            'chnk_per_m2' = 'fish/m^2')) %>%
#   select(Model = model,
#          Response = response,
#          R2)

mod_fit_df %>%
  group_by(response) %>%
  nest() %>%
  mutate(comp_full = map(data,
                         .f = function(x) {
                           lm(pred_full ~ obs,
                              data = x)
                         }),
         comp_no_champ = map(data,
                             .f = function(x) {
                               lm(pred_no_champ ~ obs,
                                  data = x)
                             })) %>%
  mutate(r2_full = map_dbl(comp_full,
                      .f = function(x) summary(x)$r.squared),
         r2_adj_full = map_dbl(comp_full,
                           .f = function(x) summary(x)$adj.r.squared),
         r2_no_champ = map_dbl(comp_no_champ,
                           .f = function(x) summary(x)$r.squared),
         r2_adj_no_champ = map_dbl(comp_no_champ,
                               .f = function(x) summary(x)$adj.r.squared)) %>%
  ungroup() %>%
  select(response, starts_with("r2")) %>%
  gather(type, r2, -response) %>%
  mutate(model = if_else(grepl('no_champ', type),
                         'non-CHaMP',
                         'CHaMP'),
         type = if_else(grepl('adj', type),
                        'Adjusted R2',
                        'R2')) %>%
  spread(type, r2) %>%
  mutate(response = recode(response,
                           'chnk_per_m' = 'fish/m',
                           'chnk_per_m2' = 'fish/m^2')) %>%
  select(Model = model,
         Response = response,
         R2, `Adjusted R2`) %>%
  kable(caption = "Summary of model fit for each of the extrapolation models to extrapolate quantile regression forest (QRF) model predictions of spring/summer Chinook parr capacity to larger scales (e.g., watershed, population).",
        digits = c(NA, NA, 3, 3))
